Ben-Shahar, O., and Zucker, S.W., General Geometric Good Continuation: A Biologically Plausible Network Model", {\em Second International Conference on Neural Networks and Brain} (ICNN\&B'05), Beijing, October 13-15, 2005.
Ben-Shahar, O., Li, G., and Zucker, S.W., Connection Geometry, Color, and Stereo, {\em  The 12th International Conference on Computer Analysis of Images and Patterns} Vienna,  Austria, August 27th - August 29th, 2007.
Alexander, E., Holtmann-Rice, D., Fleming, R., and Zucker, S.W., When Color Flows With Shading: Grounding Shape and Material Inference, {\em Vision Sciences Society Annual Meeting}, 10 - 15 May, 2013, Naples.
Dimitrov, P, and Zucker, S.W., Pattern formation in plants, 2: facilitated transport, constant gradient hypothesis, and long-distance communication, {\em Plant Vascular Development}, Banff, Alberta, 8 - 10 May, 2009.
Dobbins, A., Zucker, S.W., and Cynader, M., A mean field model of optic flow by MT neurons, {\it 20$^{th}$ Annual Meeting of the Society for Neuroscience}, 1990.
Hart, J., Avrunin, E.R., Golub, D., Scassellati, B., and Zucker,	S.W. Incorporating active vision into the body schema, {\em HRI '08:} Proceedings of the 4th ACM/IEEE International Conf. on Human robot interaction, La Jolla, March 2008.
Hart, J., Scassellati, B., and Zucker, S.W., Calibrating the Eye Motion of an Humanoid Robot, {\em IEEE $7^{\mathrm{th}}$ Int. Conf. on Development and Learning}, Monterey, CA, 9 - 12 Aug 2008.
Holtmann­Rice, D., Alexander, E., Fleming, R.W., and Zucker, S.W., When Shading Flows With Color: Making Depth Disappear, {\em Vision Sciences Society Annual Meeting}, 10 - 15 May, 2013, Naples.
Iverson, Lee, and Zucker, S.W., Orientation selection to optical flow: a computational perspective, {\it Proc. IEEE Workshop on Computer Vision}, Miami, 1987.
August, J., and Zucker, S.W., A field model for contour organization and partial differential equations, {\it Proc. Third Workshop on Perceptual Organization in Computer Vision} Vancouver, 8 July 2001, 1-1 -- 1-4.
Hart, J.W., Scassellati, B., and S.W. Zucker. Epipolar geometry for humanoid robotic heads. {\em Third North East Student Colloquium on Artificial Intelligence (NESCAI08).} Ithaca, NY, May 2008.
Hart, J.W., Scassellati, B., and S.W. Zucker. Estimating the kinematics of unseen joints that affect the stereo vision system. {\em 4th Annual New England Manipulation Symposium.} Providence, RI, May 2008.
Siddiqi, K., Tannenbaum, A., and S. Zucker, W., A Hamiltonian approach to the Eikonal equation, {\em EMMCVPR'99} York, U.K., 1999; in Pelillo, M., and Hancock, E., (eds.), {\bf Energy Minimization Methods in Computer Vision and Pattern Recognition}, Lecture Notes in Computer Science, Springer Verlag, to appear.
Siddiqi, K., Berube, Y., Tannenbaum, A., and S.W. Zucker. Shape Perception, Shocks and Wiggles. In {\em Third International Workshop on Visual Form, Capri, Italy, May, 1997}.
Kimia, B., Tannenbaum, A., and Zucker, S.W., Conservation Laws and the Evolution of Shape, {\it Human/Machine Vision Workshop, SPIE Meetings} Falmouth, MA, 1989.
Kimia, B., Tannenbaum, A., and Zucker, S.W., Toward a computational theory of shape: An overview, {\it Proc. $1^{st}$ European Conf. on Computer Vision}, Antibes, France, April, 1990. O. Faugeras (ed.), Lecture Notes in Computer Science, 427, Springer Verlag, New York.
Kunsberg, B., and Zucker, S.W., The Differential Geometry of Shape from Shading:  Biology reveals curvature structure, {\em Workshop on Perceptual Organization in Computer Vision} at IEEE Conf. on Computer Vision and Pattern Recognition, 16 June 2012, Providence.
Le, Minh Tam, Sweeney, J., Liberty, E. and Zucker, S.W., Similarity Kernels via Bi-Clustering for Conventional Intergovernmental Organizations, Current Issues in Predictive Approaches to Intelligence and Security Analytics (PAISA-10), {\em IEEE Intelligence and Security Informatics Conference}, Vancouver, 26 May, 2010.
Le, Minh-Tam, Russett, B., Sweeney, J., and Zucker, S.W. A Kernel Analysis of Kant's Conjecture, {\em 4th Annual Political Networks Conference}, University of Michigan, Gerald R. Ford School of Public Policy, June 14-18, 2011.
Le, Minh-Tam, Sweeney, J., Russett, B., and Zucker, S.W., Structural Inference in Political Science Datasets. {\em Proc. IEEE ISI Intelligence and Security Informatics}, Washington, DC, 11 - 14 June, 2012.
Minh-Tam Le, John Sweeney, Matthew Lawlor and Steven Zucker, W., Discovering Thematic Structure in Political Datasets, {\em Proc. IEEE ISI Intelligence and Security Informatics}, June 4-7, 2013, Seattle, WA.
Ben-Shahar, O., and Zucker, S.W., Flowing Toward Coherence: On the geometry of texture and shading flows, {\it Proc. Third Workshop on Perceptual Organization in Computer Vision} Vancouver, 8 July 2001, 5-1 -- 5-4.
Roland Fleming, W., Romain Vergne and Steven W. Zucker Predicting the effects of illumination on shape from shading {\em Vision Sciences Society Annual Meeting},  10 - 15 May, 2013, Naples.
Zucker, S., Complexity and confusion in computational vision, {\em Proc. $11^{th}$ Scandanavian Conference on Image Analysis}, Kangerlussuaq, Greenland, June, 1999, 1 - 10.
Sander, P, and Zucker, S.W., Tracing surfaces and surfacing traces, {\it International Conference on Computer Vision}, London, June, 1987.
Sander, P., and Zucker, S.W., Charting surface structure, {\it Proc. $1^{st}$ European Conf. on Computer Vision}, Antibes, France, April, 1990. O. Faugeras (ed.), Lecture Notes in Computer Science, 427, Springer Verlag, New York.
Sander, P., and Zucker, S.W., On computing principal directions as cross sections of fibre bundles, {\it Proc. $9^{th}$ Int. Conf. on Pattern Recognition}, 1988.
Sander, P., and Zucker, S.W., Singularities of principal direction fields from 3-D images, {\it Proc. $2^{nd}$ Int. Conf. on Computer Vision}, Tarpon Springs, Fla, 1988.
Shic, F., Chawarska, K., Zucker, S.W., and Scassellati, B., Fractals from fixations, {\em $41^{st}$ Mathematical Psychology Conference}, Washington, D.C., 26 - 29 July, 2008.
Tsotsos,J.K., Covvey,H.D., Mylopoulos,J., Zucker, S.W., Wigle, E.D.,  ``ALVEN: A System for LV Segmental Wall Motion Analysis", {\it Proc. of IEEE Computers in Cardiology}, Geneva, Sept. 1979, p445-446.
Zucker, Robert A,  Cranford, James, Zucker, Steven W., and Dimitris Metaxas, N., Discovering Control Variables for Maladaptive Drinking Behavior by Stochastic Model Analysis of Social Interaction, {\em First Annual Conference Collaborative Perspectives on Addiction,} Div 28/50, American Psychological Association, 3 May, 2013, Atlanta.
Zucker, S.W., David, C., Dobbins, A., and Iverson, L., The organization of curve detection: Coarse tangent fields and fine spline coverings, {\it Proc. $2^{nd}$ Int. Conf. on Computer Vision}, Tarpon Springs, Fla, 1988.
